rawPaper

### 2020-11-05 analysis/paper/rawPaper.Rmd
tree almost done1

# add.scale.bar(cex = 0.7, font = 2, col = "red")

#plot(bsTree, type = "phylogram", use.edge.length = FALSE, show.node.label = TRUE, label.offset = 10,  node.depth = 1)

@@

# editing/visualizing the tree
tree2 <-ggtree(tree, size = .4) + geom_treescale(x=0, y=-1.5, offset = -4) + geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) > 70), size = 3, col= "black", vjust = -0.3, hjust=1.9, na.rm = FALSE) + geom_cladelabel(node=206, label="Sicydium plumieri", color="red") + geom_cladelabel(node=113, label="Sicydium brevifile", color="blue") + geom_cladelabel(node=307, label="Sicydium salvini", color="purple") + geom_cladelabel(node=314, label="Sicydium punctatum", color="brown") + geom_cladelabel(node=363, label="Sicydium buscki", color="black") + geom_cladelabel(node=312, label="Sicydium crenilabrum", color="pink") + geom_hilight(node=369, fill="green") + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))

tree2
+ ggplot2::xlim(0, 0.06) + xlim(0, 1) 
geom_nodelab(size = 7, col= "red") + theme_tree2() + ylim(0,15)

ggtree(tree) + geom_text2(aes(subset = !isTip, label=label))
# ggtree(tree) + geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) > 80))
plot(bsTree, no.margin = TRUE, cex = 0.5)
add.scale.bar(bsTree, lwd = 1, cex = 0.7, font = 2, col = "red")

>>>>

@@

# editing/visualizing the tree
tree2 <-ggtree(tree, size = .4) + 
  geom_treescale(x=0, y=-1.5, offset = -4) + 
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) > 70), size = 3, col= "black", vjust = -0.3, hjust=1.9, na.rm = FALSE) + 
  geom_nodepoint(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) > 70), size = 1, col= "black") + 
  geom_cladelabel(node=206, label="Sicydium plumieri", color="red", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=113, label="Sicydium brevifile", color="blue", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=307, label="Sicydium salvini", color="purple", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=314, label="Sicydium punctatum", color="brown", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=363, label="Sicydium buscki", color="black", hjust = -0.07, fontsize = 3.5, offset = 0.002, fontface="italic") + 
  geom_cladelabel(node=312, label="Sicydium crenilabrum", color="orange", hjust = -0.07, fontsize = 3.5, offset = 0.004, fontface="italic") + 
  geom_hilight(node=369, fill="green") + 
  theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))

tree2
